On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-05-14 main.tex
Explanation: W(\pi_i,V(f^A)) \not =W(\pi_i,V)^A

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
\acmBooktitle{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\keywords{Real algebraic geometry, transversality, Noether
  position, bit complexity}

@@

In general, we cannot say much about the geometry of $W(\pi_i,V)$, but
if we apply a generic change of coordinates $\mA$, $W(\pi_i,V)$ is
then known to be equidimensional of dimension $(i-1)$ or
empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
  position}~\cite{EMP} (background notions in algebraic geometry are
in~\cite{Mumford76,Shafarevich77,ECA}; we will recall key
definitions). If this is the case, it suffices to choose arbitrary
$\sigma_1,\dots,\sigma_{n-1}$ in $\Q$, and solve the systems defined
by
\begin{equation}\label{eq:syst}
X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1}, f, \frac{\pa f}{\pa
  X_{i+1}} ,\dots,\frac{\pa f}{\pa X_n},  
\end{equation}
for $i=1,\dots,n$.  They all admit finitely many solutions, and
Theorem~2 in~\cite{EMP} proves that the union of their solution sets
contains one point on each connected component of $V \cap \R^n$.

@@

>>>>

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
\acmBooktitle{Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\keywords{Real algebraic geometry; weak transversality; Noether
  position; complexity }

@@

In general, we cannot say much about the geometry of $W(\pi_i,V)$, but
if we apply a generic change of coordinates $\mA$ to $f$, then $W(\pi_i,V)$ is
known to be equidimensional of dimension $(i-1)$ or
empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
  position}~\cite{EMP} (background notions in algebraic geometry are
in~\cite{Mumford76,Shafarevich77,ECA}; we will recall key
definitions). If this is the case, it suffices to choose arbitrary
$\sigma_1,\dots,\sigma_{n-1}$ in $\Q$, and solve the systems defined
by
\begin{equation}\label{eq:syst}
X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1}, f, \frac{\pa f}{\pa
  X_{i+1}} ,\dots,\frac{\pa f}{\pa X_n},  
\end{equation}
for $i=1,\dots,n$.  They all admit finitely many solutions, and
Theorem~2 in~\cite{EMP} proves that the union of their solution sets
contains one point on each connected component of $V \cap \R^n$.

@@

Note that for a variety $Y \subset \C^n,$ we can define $Y^{\mA}$ as the image of $Y$ by the map $\phi_{\mA} : \xb \mapsto \mA^{-1}\xb.$ Note that $W(\pi_i,V(f^\mA))$ may not equal $W(\pi_i,V(f))^\mA$, as, for instance, their dimensions may vary.
